On the computational complexity of detecting possibilistic locality

### 2017-06-20 paper.tex
Remove instance of "this" before theorem 1 per referee comment.

Question: do there exist a set of functions $T_i$, such that the $T_i$ are deterministic, and $T=\sum_i T_i$?
\end{defn}
Tihs represents a two-party nonlocality scenario in which Alice has access to measurements with $m$ outcomes, and Bob has access to measurements with $l$ outcomes. We are given a possibility table and asked whether or not it displays nonlocality. In general, we will take $|A|=|B|=n$ to maintain a single scaling factor; in fact this change is without loss of generality. In the case where $l=m$, we will denote this problem merely $l$-\textsc{PossLoc}. While this is not essential, we will also require that the data tables obey the possibilistic no-signalling principle; this merely streamlines the wording of the theorems. 
\begin{thm} \cite{Mans2017}
2-\textsc{PossLoc} is in \textbf{P}.
\end{thm}
\begin{proof}
This proof proceeds by showing that the only kind of possibilistic nonlocality that can occur in the two-outcome case is the one originally identified by Hardy \cite{Hard1993}; that is to say, a feature of the following kind, in which a blank space can be substituted either for a 0 or for a 1:
\begin{equation*}
\begin{array}{c| c c | c c |}
&&&&\\ \hline
&1 & & 0 & \\
&& & & \\ \hline
&0& & &  \\
&& & & 0 \\ \hline
\end{array}
\end{equation*}
We can quickly see that the highlighted one is impossible to extend to a ``deterministic grid'', \emph{i.e.} no single deterministic hidden variable can account for that possibility without also introducing an event that is impossible in the diagram. Since the appearance of this structure is equivalent to possibilistic nonlocality in this case, an algorithm to determine whether or not a given data table is possibilistically local or nonlocal reduces to checking each possible set of four contexts of this type, of which there are $n^2(n-1)^2/4$. Since checking for the appearance of such structures is possible in constant time, our algorithm runs in $O(n^4)$.
\end{proof}
However, this argument is specific to the case in which we have measurements with at most two outcomes on each side. As an illustration that there are quantumly-accessible nonlocal data tables that are not reducible to a fine-graining of a Hardy paradox, we will now demonstrate a novel possibilistic nonlocality scenario in the (2,3) case. This will be a generalisation of Hardy's proof of Bell's theorem.

>>>>

Question: do there exist a set of functions $T_i$, such that the $T_i$ are deterministic, and $T=\sum_i T_i$?
\end{defn}
Tihs represents a two-party nonlocality scenario in which Alice has access to measurements with $m$ outcomes, and Bob has access to measurements with $l$ outcomes. We are given a possibility table and asked whether or not it displays nonlocality. In general, we will take $|A|=|B|=n$ to maintain a single scaling factor; in fact this change is without loss of generality. In the case where $l=m$, we will denote this problem merely $l$-\textsc{PossLoc}. While it is not essential, we will also require that the data tables obey the possibilistic no-signalling principle; this merely streamlines the wording of the theorems. 
\begin{thm} \cite{Mans2017}
2-\textsc{PossLoc} is in \textbf{P}.
\end{thm}
\begin{proof}
This proof proceeds by showing that the only kind of possibilistic nonlocality that can occur in the two-outcome case is the one originally identified by Hardy \cite{Hard1993}; that is to say, a feature of the following kind, in which a blank space can be substituted either for a 0 or for a 1:
\begin{equation*}
\begin{array}{c| c c | c c |}
&&&&\\ \hline
&1 & & 0 & \\
&& & & \\ \hline
&0& & &  \\
&& & & 0 \\ \hline
\end{array}
\end{equation*}
We can quickly see that the highlighted one is impossible to extend to a ``deterministic grid'', \emph{i.e.} no single deterministic hidden variable can account for that possibility without also introducing an event that is impossible in the diagram. Since the appearance of this structure is equivalent to possibilistic nonlocality in this case, an algorithm to determine whether or not a given data table is possibilistically local or nonlocal reduces to checking each possible set of four contexts of this type, of which there are $n^2(n-1)^2/4$. Since checking for the appearance of such structures is possible in constant time, our algorithm runs in $O(n^4)$.
\end{proof}
However, this argument is specific to the case in which we have measurements with at most two outcomes on each side. As an illustration that there are quantumly-accessible nonlocal data tables that are not reducible to a fine-graining of a Hardy paradox, we will now demonstrate a novel possibilistic nonlocality scenario in the (2,3) case. This will be a generalisation of Hardy's proof of Bell's theorem.
